---
title: "Satisfaction with democracy"
author: "Michael Škvrňák"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(dplyr)
library(targets)
library(sjPlot)

```

Hypotheses from pre-analysis plan:  

- Hypothesis 1: Pre-Election satisfaction does not matter for participation when socio-demographic controls and other attitudinal drivers of participation are controlled for.  
- Hypothesis 2: Voter Turnout is more strongly associated with post-election satisfaction than pre-election satisfaction.  
- Hypothesis 3: Elections increase satisfaction with democracy among voters, but exert no effect on abstainers.  
- Hypothesis 4: The strongest increase is among those, whose preferred candidates qualified for the 2nd round (1st round of voting) or won the second round (2nd round of voting).  
- Hypothesis 5: The effect of winning is stronger for respondents with stable preferences.  


# Czech Republic, parliamentary election 1996

```{r}
tar_load(cz_96_merged)
```

## H1
```{r}

```


## H2
```{r}
lm2_1 <- lm(voted ~ swd_w1, data = cz_96_merged %>% filter(both_waves))
lm2_2 <- lm(voted ~ swd_w2, data = cz_96_merged %>% filter(both_waves))
lm2_3 <- lm(voted ~ swd_w1 + swd_w2, data = cz_96_merged %>% filter(both_waves))

tab_model(list(lm2_1, lm2_2, lm2_3))
```

## H3
```{r}
lm3_1 <- lm(swd_diff ~ voted, data = cz_96_merged %>% filter(both_waves))
lm3_2 <- lm(swd_diff ~ voted + swd_w1, data = cz_96_merged %>% filter(both_waves))

tab_model(list(lm3_1, lm3_2))
```

## H4
Applicable only to presidential election.

## H5
```{r}
lm5_0 <- lm(swd_diff ~ winner_government + stable_voter + swd_w1, 
            data = cz_96_merged %>% filter(both_waves))
lm5_1 <- lm(swd_diff ~ winner_government * stable_voter + swd_w1, 
            data = cz_96_merged %>% filter(both_waves))

tab_model(list(lm5_0, lm5_1))
```

